Chemistry of the Orphan Stream I: Identifying Stream Candidates with Low Resolution Spectroscopy

### 2012-09-04 2012-oss-mrs/draft-oss-mrs.tex
Incorporated comments and suggestions by GDC

\author{Andrew R. Casey\altaffilmark{1,2}, Stefan C. Keller\altaffilmark{1}, Gary Da Costa\altaffilmark{1}, Elizabeth Maunder\altaffilmark{1}}
\altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; \email{arcasey@mso.anu.edu.au}}
\altaffiltext{2}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
77 Massachusetts Avenue, Cambridge, MA 02139, USA}

\begin{abstract}
We present coordinates and properties of candidate K giant members in the Orphan Stream, which have been identified from low resolution spectroscopic data taken with AAOmega on the Australian Astronomical Telescope. With modest S/N and independent cuts in photometry, kinematics, gravity and metallicity we yield self-consistent, highly probable stream members. Our data indicates an overall stream metallicity of [Fe/H] $= -1.74 \pm 0.05$ which is more metal-rich than previously found and unbiased by spectral type. We find a revised stream distance of 24 kpc near the celestial equator, and our kinematic signature peaks at $V_{helio} \sim 218$\,km s$^{-1}$. We highlight likely members for high resolution spectroscopic follow-up.
\end{abstract}

@@

The Orphan Stream was independently detected by both \citet{Grillmair;Dionatos_2006} and \citet{Belokurov;et-al_2006}, and is distinct from other substructures in the halo. The stream stretches over $60\,^\circ$ in the sky, has a low surface brightness and a narrow stream width of only $\sim2^\circ$ and as the name suggests, the parent object largely remains a mystery. The stream extends past the celestial equator \-- outside the SDSS footprint \-- but is not detected in existing southern surveys \citep{Newberg;et-al_2010}. Whilst the parent system remains elusive, significant effort has been placed on associating the stream with known Milky Way satellites \citep{Zucker;et-al_2006, Fellhaur;et-al_2007,Jin;Lynden_Bell_2007,Sales;et-al_2008}. In contrast, there has been relatively limited observational work on the Orphan Stream itself other than the original discovery papers \citep{Grillmair;Dionatos_2006, Belokurov;et-al_2006, Belokurov;et-al_2007} and the work of \citet{Newberg;et-al_2010}. This is largely to be expected given the absence of multi-band photometry in the southern sky, the difficulty in reliably separating Orphan Stream members from halo stars and the low luminosity of stream members. It is unlikely the full extent of the Orphan Stream will be detected until the SkyMapper telescope surveys this region \citep{Keller;et-al_2007}.

@@

In this letter we present a detailed, self-consistent analysis to identify K giant members of the Orphan Stream. Using our selection method we have catalogued the locations of seven highly probable Orphan Stream candidates, all worthy of high resolution spectroscopic follow up. In the following section we outline our photometric target selection. In Section \S\ref{sec:observations} we describe the low resolution spectroscopic observations. The data analysis, including stream identification, is discussed in \S\ref{sec:analysis} and in \S\ref{conclusions} the conclusions, predictions and future work are presented.

@@

The Orphan Stream is closest to us in two locations on the edge of the SDSS footprint: at the celestial equator \citep{Belokurov;et-al_2007}, and along outrigger SEGUE Stripe 1540 \citep{Newberg;et-al_2010}. These two locations are unequivocally the best place to recover bright stream members. We have targeted two fields centered on ($\alpha$, $\delta$) = (10:48:15, 00:00:00) and (10:48:15, -02:30:00), and employed a combination of colour cuts with the SDSS DR 7 \citep{Abazajian;et-al_2009} data set in order to identify likely K giants:

\begin{eqnarray}
(g - i)_0 &>& 0.6 \\
0.86i_0 + 3.30 >& g_0 &> 0.95i_0 + 1.35 \\
19.00 >& g &> 15.75
\end{eqnarray}

\textbf{Stefan can you see if you can find your original selection SQL \-- I deduced these relationships from cross-matching against SDSS and fitting boundary lines.}

@@

\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/vgsr-histogram.pdf}
	\caption{Galactocentric rest frame velocities for our observed sampled (grey), and predicted  Besan\c{c}on velocities (white) which have been scaled to match our observed sample size. The expected kinematic signature from \citet{Newberg;et-al_2010} for the Orphan Stream is highlighted, as is our kinematic selection window (green).}
	\label{fig:velocities}
\end{figure}

@@

We have measured the equivalent widths of the Ca\,\textsc{II} near-infrared triplet lines for stars which meet our kinematic and surface gravity criteria. After correcting for luminosity, the equivalent width of the Ca\,\textsc{II} triplet lines provide a good indication for the metallicity of a RGB star \citep{Amandroff;Da_Costa_1991}. We have employed the \citet{Starkenburg;et-al_2010} relationship and corrected for luminosity in $g$ against the horizontal branch magnitude at $g_0$ = 17.1 \citep{Newberg;et-al_2010}. Strictly speaking, the Ca\,\textsc{II}-[Fe/H] calibation is only valid for stars brighter than the horizontal branch, although the relationship only becomes significantly inappropriate near $g \-- g_{HB} \sim +1$ \citep{Savine;et-al_2012}. Many of our candidates are fainter than this valid luminosity range, and therefore they should not be excluded solely because of their derived metallicities. Stars fainted than $g_0$ will have slightly lower metallicities than predicted by our Ca\,\textsc{II}-[Fe/H] relationship, and for these stars we will only use metallicities to assign a relative qualitative likelihood for stream membership.

\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/cmd.pdf}
	\caption{Color magnitude diagram showing our observed candidates (grey) and highlighting candidates which meet our kinematic and gravity cuts. Candidates are colored by their metallicity, and those with upper limiting gravities are marked as triangles. Highly probable stream members are marked. Relevant 10 Gyr \citet{Girardi;et-al_2008} isochrones at $[\mbox{Fe/H}] = -1.5$ (dotted), $-2.0$ (dashed) at 21.4\,kpc \citep{Newberg;et-al_2010} are shown, as well as our best-fitting 10 Gyr isochrone of $[\mbox{Fe/H}] = -1.74$ at 24\,kpc (solid).}
	\label{fig:cmd}
\end{figure}

Figure \ref{fig:cmd} illustrates all eighteen candidates which meet both our kinematic and surface gravity criterion. Candidates are coloured by their metallicity deduced from the Ca\,\textsc{II} triplet. There are four candidates above $g_0 \sim 17.1$ which are within our valid luminosity range. One of these objects at $(g \-- r, g) \sim (0.57, 17)$ is +0.64\,dex more metal-rich than expected for the stream, and is excluded from membership. Another is only +0.21\,dex more metal-rich and sits at (0.57, 16.1), but it's position relative to the isochrone is inconsistent with our inferred metallicity. There appears to be an extremely metal-poor star in this sample with an estimated $[\mbox{Fe/H}] = -2.70$ which may be associated with the Orphan Stream. The likely parent system of the Orphan Stream is a Milky Way dwarf spheroidal \citep{Belokurov;et-al_2007, Sales;et-al_2008}, which are known to have a wide metallicity distribution function \citep{Tafelmayer;et-al_2010, Tolstoy;et-al_2009}, including an over-represented population of extremely metal poor stars \citep{Frebel;et-al_2010, Kirby;et-al_2010}. Thus, we keep this extremely metal-poor star as a potential stream member for follow-up chemical analysis. 
% speak about OSS 1?

\citet{Newberg;et-al_2010} found the median Orphan Stream metallicity to be [Fe/H] $= -2.1$ from BHB stars, and a distance of $21.4 \pm 1.0$\,kpc in this region. In Figure \ref{fig:cmd} we have overlaid 10 Gyr old isochrones from \citet{Girardi;et-al_2008} with metallicities of [Fe/H] $= -2.0$ and $-1.5$ at a distance of $21.4$ kpc \citep{Newberg;et-al_2010}. Four of our most probable Orphan Stream members fall between these isochrones. Assuming the three highly probable members outside our valid luminosity range are over-predicted by $\sim+0.1$ dex [citation needed], when combining our four Orphan Stream members we yield a stream metallicity of $[\mbox{Fe/H}] = -1.74 \pm 0.05$. This is slightly more metal-rich than the $[\mbox{Fe/H}] =-2.1$ found by \citet{Newberg;et-al_2010} from BHB stars.

@@

\begin{deluxetable*}{lcccccccccl}
\tabletypesize{\scriptsize}
\tablecaption{Identified Orphan Stream Members\label{tab:oss-members}}
\tablehead{
	\colhead{Star} &
	\colhead{$\alpha$} &
	\colhead{$\delta$} &
	\colhead{$g$} &
	\colhead{$g \-- r$} &
	\colhead{$V_{helio}$} &
	\colhead{$V_{\textsc{gsr}}$} &
	\colhead{$V_{err}$} &
	\colhead{$EW_{\lambda8807}$} &
	\colhead{[Fe/H]} &
	\colhead{Comment} \\
Name & (J2000) & (J2000) & & & (kms $^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$) & (\AA) & (dex)
}
\startdata
OSS 1 & 10 46 50.6 & $-$00 13 17.9 & 17.33 & 0.50  &  215.5  & \phn77.0 & 4.0 & 0.416 & -1.31 & Unlikely member! \\
OSS 2 & 10 47 17.6 & $+$00 25 07.7 & 16.09 &  0.73 &  215.7  & \phn79.2 & 3.3 & 0.212 & -1.84 & Highly probable member \\
OSS 3 & 10 47 30.1 & $-$00 01 24.6 & 17.25 &  0.61 &  221.4  & \phn83.6 & 3.4 & 0.123 & -1.62 & Highly probable member \\
OSS 4 & 10 49 08.3 & $+$00 02 00.2 & 16.27 &  0.62 &  218.5  & \phn81.5 & 4.6 & 0.034 & -2.70 & Possible EMP member \\
OSS 6 & 10 48 20.9 & $+$00 26 34.4 & 17.88 &  0.55 &  254.9  & 118.8 & 11.7 & 0.469 & -1.65 & Highly probable member \\
OSS 7 & 10 46 29.3 & $-$00 19 38.5 & 17.77 &  0.56 &  217.3  & \phn78.4 & 5.2 & 0.126 & -1.63 & Highly probable member 
\enddata
\end{deluxetable*}

@@

We have presented a detailed analysis to isolate individual Orphan Stream K giants from low resolution spectroscopy using a combination of photometric, kinematic, gravity, and metallicity information. Although each individual criterion is likely to induce some level contamination, the resulting union of these selections reveal highly probable, self-consistent, Orphan Stream K giants.  We deduce a stream metallicity of $[\mbox{Fe/H}] = -1.74 \pm 0.05$ which is not biased by spectral type. Recall that the metallicity determination was performed after kinematic and gravity cuts, and our most probable members lay perfectly on a 10 Gyr isochrone of $[\mbox{Fe/H}] = -1.74$. Our stream members indicate a revised distance to the stream of $24$\,kpc at $(l, b) = (250^\circ$, $50^\circ)$, slightly farther than that deduced by \citet{Newberg;et-al_2010}.

If the Orphan Stream continues through SEGUE stripe 1540 at $(l, b) = (271^\circ$, $38^\circ)$ as \citet{Newberg;et-al_2010} found, then the stream is even closer there than in the region analysed here. Thus, if our observations and analyses are repeated at $(271^\circ$, $38^\circ)$, we predict brighter (and subsequently more numerous) K giant stream members will be recovered.

>>>>

\author{Andrew R. Casey\altaffilmark{1,2}, Stefan C. Keller\altaffilmark{1}, Gary Da Costa\altaffilmark{1}, Elizabeth Maunder\altaffilmark{1}, Anna Frebel\altaffilmark{2}}
\altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; \email{arcasey@mso.anu.edu.au}}
\altaffiltext{2}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
77 Massachusetts Avenue, Cambridge, MA 02139, USA}

\begin{abstract}
We present coordinates and properties of candidate K giant members in the Orphan Stream, which have been identified from low resolution spectroscopic data taken with AAOmega on the Australian Astronomical Telescope. With modest S/N and independent cuts in photometry, kinematics, gravity and metallicity we yield self-consistent, highly probable stream members. Our data indicates an overall stream metallicity of [Fe/H] $= -1.78 \pm 0.08$ which is more metal-rich than previously found and unbiased by spectral type. We find a revised stream distance of 24 kpc near the celestial equator, and our kinematic signature peaks at $V_{helio} \sim 218$\,km s$^{-1}$. The Orphan Stream appears extremely cold, with an intrinsic dispersion of less than $0.3 \pm 3.3$ km s$^{-1}$. We highlight likely members for high resolution spectroscopic follow-up.
\end{abstract}

@@

The Orphan Stream was independently detected by both \citet{Grillmair;Dionatos_2006} and \citet{Belokurov;et-al_2006}, and is distinct from other substructures in the halo. The stream stretches over $60\,^\circ$ in the sky, has a low surface brightness and a narrow stream width of only $\sim2^\circ$ and as the name suggests, the parent object largely remains a mystery. The stream extends past the celestial equator \-- outside the SDSS footprint \-- but is not detected in existing southern surveys \citep{Newberg;et-al_2010}. Whilst the parent system remains elusive, significant effort has been placed on associating the stream with known Milky Way satellites \citep{Zucker;et-al_2006, Fellhaur;et-al_2007,Jin;Lynden_Bell_2007,Sales;et-al_2008}. In contrast, there has been relatively limited observational work on the Orphan Stream itself other than the original discovery papers \citep{Grillmair;Dionatos_2006, Belokurov;et-al_2006, Belokurov;et-al_2007} and the work of \citet{Newberg;et-al_2010}. This is largely to be expected given the absence of multi-band photometry in the southern sky and the total low luminosity of the stream, making it difficult in reliably identifying Orphan Stream members from halo stars. It is unlikely the full extent of the Orphan Stream will be detected until the SkyMapper telescope surveys this region \citep{Keller;et-al_2007}.

@@

In this letter we present a detailed, self-consistent analysis to identify K giant members of the Orphan Stream. Using our selection method we have catalogued the locations of seven highly probable Orphan Stream candidates, all worthy of high resolution spectroscopic follow up. In the following section we outline our photometric target selection. In Section \S\ref{sec:observations} we describe the low resolution spectroscopic observations. The data analysis, including stream identification, is discussed in \S\ref{sec:analysis} and in \S\ref{sec:conclusions} the conclusions, predictions and future work are presented.

@@

The Orphan Stream is closest to us in two locations on the edge of the SDSS footprint: at the celestial equator \citep{Belokurov;et-al_2007}, and along outrigger SEGUE Stripe 1540 \citep{Newberg;et-al_2010}. These two locations are unequivocally the best place to recover bright stream members. We have targeted two fields centered on ($\alpha$, $\delta$) = (10 48 15, 00 00 00) and (10 48 15, $-02$ 30 00), and employed a combination of colour cuts with the SDSS DR 7 \citep{Abazajian;et-al_2009} data set in order to identify likely K giants:

\begin{eqnarray}
0.6 <& (g-i)_0 &< 1.7 \\
-15(g-i)_0 + 27 <& g_0 &< -3.75(g-i)_0 + 22.5 \\
15  <& i_0  &< 18 
\end{eqnarray}

@@

\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/vgsr-histogram.pdf}
	\caption{Galactocentric rest frame velocities for stars in both our observed fields (grey), and predicted Besan\c{c}on velocities which have been scaled to match our observed sample size. The expected kinematic signature from \citet{Newberg;et-al_2010} for the Orphan Stream is highlighted, as is our kinematic selection window (green).}
	\label{fig:velocities}
\end{figure}

@@

We have measured the equivalent widths of the Ca\,\textsc{II} near-infrared triplet lines for stars which meet our kinematic and surface gravity criteria. After correcting for luminosity, the equivalent width of the Ca\,\textsc{II} triplet lines provide a good indication for the metallicity of a RGB star \citep{Amandroff;Da_Costa_1991}. We have employed the \citet{Starkenburg;et-al_2010} relationship and corrected for luminosity in $g$ against the horizontal branch magnitude at $g_0$ = 17.1 \citep{Newberg;et-al_2010}. Strictly speaking, the Ca\,\textsc{II}\---[Fe/H] calibation is only valid for stars brighter than the horizontal branch, although the relationship only becomes significantly inappropriate near $g \-- g_{HB} \sim +1$ \citep{Saviane;et-al_2012}. Many of our candidates are fainter than this valid luminosity range, and therefore they should not be excluded solely because of their derived metallicities. Stars fainted than $g_0$ will have slightly lower metallicities than predicted by our Ca\,\textsc{II}\---[Fe/H] relationship, and for these stars we will only use metallicities to assign a relative qualitative likelihood for stream membership.

\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/cmd.pdf}
	\caption{Color magnitude diagram showing our observed candidates (grey) and highlighting candidates which meet our kinematic and gravity cuts. Candidates are colored by their metallicity, and those with upper limiting gravities are marked as triangles. Highly probable stream members are marked. Relevant 10 Gyr \citet{Girardi;et-al_2008} isochrones at $[\mbox{Fe/H}] = -1.5$ (dotted), $-2.0$ (dashed) at 21.4\,kpc \citep{Newberg;et-al_2010} are shown, as well as our best-fitting 10 Gyr isochrone of $[\mbox{Fe/H}] = -1.78$ at 24\,kpc (solid).}
	\label{fig:cmd}
\end{figure}

Figure \ref{fig:cmd} illustrates all eighteen candidates which meet both our kinematic and surface gravity criterion. Candidates are coloured by their metallicity deduced from the Ca\,\textsc{II} triplet. There are four candidates above $g_0 \sim 17.1$ which are within our valid luminosity range. One of these objects at $(g \-- r, g) \sim (0.57, 17)$ is +0.64\,dex more metal-rich than expected for the stream, and is excluded from membership. Another is only +0.21\,dex more metal-rich and sits at (0.57, 16.1), but it's position relative to the isochrone is inconsistent with our inferred metallicity. There appears to be an extremely metal-poor star in this sample with an estimated $[\mbox{Fe/H}] = -2.70$ which may be associated with the Orphan Stream. The likely parent system of the Orphan Stream is a Milky Way dwarf spheroidal \citep{Belokurov;et-al_2007, Sales;et-al_2008}, which are known to have a wide metallicity distribution function \citep{Tolstoy;et-al_2009}, including populations of extremely metal-poor stars \citep{Kirby;et-al_2010,Frebel;et-al_2010,Tafelmeyer;et-al_2010}. Thus, we keep this extremely metal-poor star as a potential stream member for follow-up chemical analysis. 
% speak about OSS 1?

\citet{Newberg;et-al_2010} found the median Orphan Stream metallicity to be [Fe/H] $= -2.1$ from BHB stars, and a distance of $21.4 \pm 1.0$\,kpc in this region. In Figure \ref{fig:cmd} we have overlaid 10 Gyr old isochrones from \citet{Girardi;et-al_2008} with metallicities of [Fe/H] $= -2.0$ and $-1.5$ at a distance of $21.4$ kpc \citep{Newberg;et-al_2010}. Four of our most probable Orphan Stream members fall between these isochrones. The brightest of these green points has an abundance which is in good agreement with the isochrone value. The line strength abundances for the other three stars (OSS 3, 6 and 7 \--- see Table \ref{tab:oss-members}) are less certain, as these stars are fainter than the horizontal branch.

We can ascertain abundance corrections for our stars fainter than the horizontal branch by comparing our $V-V_{HB}$ and $EW_{\lambda8452} + EW_{\lambda8662}$ with those measured by \citet{Saviane;et-al_2012} for globular clusters. Only two clusters had measured Ca \textsc{II} equivalent widths for stars fainter than the horizontal branch: NGC 6397 with $[\mbox{Fe/H}] = -1.99$ and NGC 6254 with $[\mbox{Fe/H}] = -1.57$ \citep[both abundances from][]{Carretta;et-al_2009}. OSS 6 and OSS 7 lie at the mid-point between these cluster stars, implying an abundance of $[\mbox{Fe/H}] \sim -1.78$, or a mean correction of $-0.14$ dex for OSS 6 and 7. Although OSS 3 is 0.15 magnitudes fainter than the horizontal branch, it has equivalent widths consistent with our inferred metallicity of $[\mbox{Fe/H}] = -1.62$, so no correction was made. With corrections included for OSS 6 and 7 we find a median stream metallicity from our four most probable stars of $[\mbox{Fe/H}] = -1.78 \pm 0.08$, which is slightly more metal-rich than the $[\mbox{Fe/H}] =-2.1$ found by \citet{Newberg;et-al_2010} from BHB stars. If we include our EMP candidate, the median decreases by 0.01 dex and the spread increases to 0.39\,dex.

@@

\begin{deluxetable*}{lcccccccccl}
\tabletypesize{\scriptsize}
\tablecaption{Identified Orphan Stream Members\label{tab:oss-members}}
\tablehead{
	\colhead{Star} &
	\colhead{$\alpha$} &
	\colhead{$\delta$} &
	\colhead{$g$} &
	\colhead{$g \-- r$} &
	\colhead{$V_{helio}$} &
	\colhead{$V_{\textsc{gsr}}$} &
	\colhead{$V_{err}$} &
	\colhead{$EW_{\lambda8807}$} &
	\colhead{[Fe/H]} &
	\colhead{Comment} \\
Name & (J2000) & (J2000) & & & (kms $^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$) & (\AA) & (dex)
}
\startdata
OSS 1 & 10 46 50.6 & $-$00 13 17.9 & 17.33 & 0.50  &  215.5  & 77.0 & 4.0 & 0.416 & $-1.31$ & Unlikely member! \\
OSS 2 & 10 47 17.6 & $+$00 25 07.7 & 16.09 &  0.73 &  215.7  & 79.2 & 3.3 & 0.212 & $-1.84$ & Highly probable member \\
OSS 3 & 10 47 30.1 & $-$00 01 24.6 & 17.25 &  0.61 &  221.4  & 83.6 & 3.4 & 0.123 & $-1.62$ & Highly probable member \\
OSS 4 & 10 49 08.3 & $+$00 02 00.2 & 16.27 &  0.62 &  218.5  & 81.5 & 4.6 & 0.034 & $-2.70$ & Possible EMP member \\
OSS 6 & 10 48 20.9 & $+$00 26 34.4 & 17.88 &  0.55 &  254.9  & 118.8 & 11.7 & 0.469 & $-1.79$\tablenotemark{a} & Highly probable member \\
OSS 7 & 10 46 29.3 & $-$00 19 38.5 & 17.77 &  0.56 &  217.3  & 78.4 & 5.2 & 0.126 & $-1.77$\tablenotemark{a} & Highly probable member 
\enddata
\tablenotetext{a}{Abundance correction of $-0.14$\,dex included (see \S\ref{sec:metallicities}).}
\end{deluxetable*}

@@

We have presented a detailed analysis to isolate individual Orphan Stream K giants from low resolution spectroscopy using a combination of photometric, kinematic, gravity, and metallicity information. Although each individual criterion is likely to induce some level contamination, their intersection reveals highly probable, self-consistent, Orphan Stream K giants.  We deduce a stream metallicity of $[\mbox{Fe/H}] = -1.78 \pm 0.08$ which is not biased by spectral type. Recall that the metallicity determination was performed after kinematic and gravity cuts, and our most probable members lay perfectly on a 10 Gyr isochrone of $[\mbox{Fe/H}] = -1.78$. Our stream members indicate a revised distance to the stream of $24$\,kpc at $(l, b) = (250\,^\circ$, $50\,^\circ)$, slightly farther than that deduced by \citet{Newberg;et-al_2010}.

If the Orphan Stream continues through SEGUE stripe 1540 at $(l, b) = (271\,^\circ$, $38\,^\circ)$ as \citet{Newberg;et-al_2010} found, then the stream is even closer there than in the region analysed here. Thus, if our observations and analyses are repeated at $(271\,^\circ$, $38\,^\circ)$, we predict K giant stream members of brighter apparent magnitude will be recovered. If the stream density is similar to or higher than what we observe at $(l, b) = (250\,^\circ, 50\,^\circ)$ then more K giant Orphan Stream members are likely to be recovered in the stripe 1540 field.

Although OSS 6 has an uncertain radial velocity, using a maximum-likelihood estimation we find the mean stream galactocentric velocity at $(l, b) = (250\,^\circ, 50\,^\circ)$ from five stars to be $V_{GSR} = 82 \pm 1.6$ km s$^{-1}$ and the intrinsic dispersion to be $0.3 \pm 3.3$ km s$^{-1}$. For our four stars with low radial velocity errors this dispersion is found to be $0.00 \pm 2.4$ km s$^{-1}$. These velocities indicate that the Orphan Stream is a very cold stream, and implies their motion is largely perpendicular to the line of sight.
